---
format: gfm
---


```{r}
#| label: setup
#| echo: false
#| results: "hide"
#| warning: false
#| message: false
# Load some libraries
library("knitr")
library("RefManageR")
library("tidyverse")
library("here")
library("patchwork")
library("scholar")
library("textutils")

# Plotting options
opts_chunk$set(
  out.width = "100%", 
  dpi = 300, 
  fig.asp = .56, 
  fig.retina = 2
)

my_theme <- function() {
  theme_minimal() + 
    theme(
      plot.title = element_text(size = rel(1), face = "bold"), 
      plot.subtitle = element_text(size = rel(0.9)),
      plot.caption = element_text(color = "#777777", vjust = 0),
      axis.title = element_text(size = rel(.9), hjust = 0.95, face = "italic"), 
      panel.grid.major = element_line(linewidth = rel(.1), color = "grey70"), 
      panel.grid.minor = element_line(linewidth = rel(.1), color = "grey70")
    )
}

```

# mybib

**Last Updated**: `r sprintf("%s", Sys.time())`  
**License**: Public Domain (CC-0)

Version controlled .bib files for my scholarly work, as well as some light analyses and a complete reference list.

This repo now includes two main bib files: 
__publications_html.bib__ and __publications_latex.bib__. 

I call these files in to other projects (e.g., cv, personal website) when I want to print a list of references. 

Initial commit is a direct copy from [Joseph Casillas](https://github.com/jvcasillas/mybib). 

----





Load bibs and generate some useful files and dataframes: 

```{r}
#| label: data
#| message: false
#| warning: false
# Load bib
bib <- suppressWarnings(
  ReadBib(
    here("publications_html.bib"), 
    check = FALSE
  )
)

# Create csv of citekeys
cite_key_list <- bind_cols(
  bib$key |> unlist() |> tibble::enframe(name = NULL), 
  bib$bibtype |> unlist() |> tibble::enframe(name = NULL), 
  bib$year |> unlist() |> tibble::enframe(name = NULL)
  ) |> 
  rename(citekey = value...1, type = value...2, year = value...3) |> 
  write_csv(here("cite_key_list.csv"))

# Set bib options for printing
BibOptions(
  bib.style = "authoryear", 
  style = "text", 
  max.names = 10, 
  first.inits = TRUE, 
  check.entries = FALSE
)

# Convert to dataframe for analyses
dat <- bib |> 
  as_tibble() |> 
  map_df(.f = HTMLdecode) |> 
  mutate(year = as.numeric(year))
```
